\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}

\section{IDAC Proposal Checklist}\label{sec:checklist}

There is a spectrum of possibilities for an \gls{IDAC}'s scope, from just hosting the \gls{Object} lite database, to serving full copies of the current data release and prompt products database.
Here an attempt is made to have a set of check lists  that can be used to look at an \gls{IDAC}.
\secref{sec:fullDAC} covers a full capability \gls{IDAC}, while  \secref{sec:liteDAC} gives the criteria for a minimum capability \gls{IDAC}.
There will undoubtedly be proposals in between. There are some criteria that any \gls{IDAC} must meet, in order to comply with Rubin Observatory data policy. These are given in \secref{sec:anyDAC}.

\subsection{Any \gls{DAC}} \label{sec:anyDAC}
\begin{todolist}
\item Authentication/Authorization system  inline with Rubin Observatory Access
\item Agreement to make broadly accessible to all Data Rights holders
\end{todolist}

\subsection{Lite \gls{IDAC}} \label{sec:liteDAC}
All criteria in \secref{sec:anyDAC}, and then, in addition:
\begin{todolist}
\item Database system capable of handling $4^{10}$ rows.
\item \gls{IVOA} \gls{TAP} interface, MyDB and Table Upload, \gls{CAOM} support.
\item About 500TB of disk for catalogs + MyDBs.
\item Professional support staff (min 0.25 \gls{FTE})
\item Sufficient connectivity to support users
\end{todolist}

\subsection{Full \gls{DAC}} \label{sec:fullDAC}
All criteria in \secref{sec:anyDAC}, and then, in addition:
\begin{todolist}
\item Staff (about 5 \gls{FTE}) to handle major hardware installation
\item Agreement to stand up standard \gls{Science Platform} (Puppet/Kubernetes etc.)
\item Database system capable of handling all catalogs (or \gls{Qserv}) with \gls{IVOA}  interfaces.
\item Understanding of sizing model in \citeds{DMTN-135} - sizing model and a cost model for the \gls{IDAC}.
\item "Commitment to fund the \gls{IDAC} through the \gls{LSST} operations period, FY22-FY34 (probably  $>\$6M/year$ based on hardware cost model and labor plan).".
\item Sufficient connectivity to support data transfer in and user access out at least 20Gbps of free bandwidth.
\end{todolist}
